\textbf{Using the MSU Thesis Class}

### 2023-05-26 docs/msu-thesis.tex
v4.1b removed idiotic colon that was required in September; updated template file

\def\msuversion{4.1}
\def\msudate{2023/05/18}
\title{\textbf{Using the MSU Thesis Class}}
\author{\textbf{Alan Munn}\\Department of Linguistics, Languages, and Cultures\\Michigan State University\\\texttt{\href{mailto:amunn@msu.edu}{amunn@msu.edu}}}
\date{Version \msuversion\\\msudate}
\usepackage{fontspec}
\usepackage[lmargin=.75in,rmargin=.75in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{titling}
\usepackage{array, booktabs, multicol, fancyhdr, xspace,tabularx}
\usepackage{enumitem}
\usepackage{fancyvrb,listings,url}
\usepackage[sf,small]{titlesec}
\usepackage[section]{placeins}
\usepackage[colorlinks=true]{hyperref}
\setmonofont{Inconsolatazi4}

@@

\section{User commands}
In addition to all the user functionality defined by \pkg{memoir}, the \pkg{msu-thesis}\ class defines seven new titling commands, and two “appeasement” commands, i.e., commands to tweak the formatting to appease the the thesis office’s inconsistency.
\begin{table}[htpb]
\centering
\begin{tabularx}{.8\textwidth}{>{\ttfamily}lX}
\toprule
{\bs maketitlepage} & Makes the main title page for the thesis.\\
{\bs fieldofstudy\{\}} &  Takes one argument corresponding to your field of study. For a dual major use the \pkg{\bs dualmajor} command instead.\\
{\bs dualmajor\{\}\{\}} & Takes two arguments, one for each of the two majors.\\
{\bs dedication\{\}} &  Takes one argument (should be short), your dedication.\\
%{\{publicabstract\}} &  Environment for the public abstract (unnumbered, uncounted).\\
{\bs makecopyrightpage} &  Creates the copyright page (use \texttt{\bs makecopyrightpage*} to align the text on the left.)\\
{\bs makededicationpage} &  Creates the dedication page.\\
%{\bs makebibliographypage} &  Creates the bibliography cover page.\\
{\{abbreviations\}} & Environment for the List of Abbreviations \\
{msutocdeph} & Counter for setting the TOC depth. Default is 1 (sections+chapters). Set this to 0 to use the simplified (chapters only) format that the thesis office suggests but doesn’t require.\\
\bottomrule
\end{tabularx}
\caption{Class titling commands}
\end{table}

\begin{table}[htpb]
\centering
\begin{tabularx}{.8\textwidth}{>{\ttfamily}lX}
\toprule
{\bs msucaptiondelim} &  Delimiter for floating elements (see section \ref{captiondelim}).\\
%{\bs setabstractnamespace} &  Changes spacing after the name in the abstract (see section \ref{abstractspacing}).\\
\bottomrule
\end{tabularx}
\caption{Appeasement commands}
\end{table}

@@

\subsubsection{New lists}
If you are using other kinds of floats such as listings, you should use the Memoir |\newlistof| command to make the relevant list. The class provides a macro |\msucaptiondelim| which can be used to make sure the formatting of the captions in the list-of-X match the setting you have for Figures and Tables.  Here is an example of how you would add a listings list. For lists of algorithms, see section \ref{algorithms} below. The following code goes in your preamble:
\begin{quote}
\begin{lstlisting}
\newlistof{listoflistings}{lol}{List of Listings}
\newfloat[chapter]{listing}{lol}{Listing}
\newlistentry{listing}{lol}{0}
\renewcommand*{\cftlistingname}{Listing\space}
\renewcommand*{\cftlistingaftersnum}{\msucaptiondelim}
\end{lstlisting}
\end{quote}

@@

\section{Acknowledgements}
Thanks to Lars Madsen, Ulrike Fischer and Peter Wilson for help with setting up parts of 
the memoir code for versions 1.0--1.4 (now eliminated due to changed requirements). Thanks 
to Wolfgang Sternefeld for supplying the \pkg{linguex}\ spacing fix code, Leo Liu for the 
landscape page numbering code, which greatly simplified my original version. Thanks to 
Florent Chervet for early \pkg{hyperref} code (up until v.3.6), and Ulrike Fischer for the 
current \pkg{hyperref} code.  Thanks also to the following students who have reported 
problems over the years: Irina Agafonova, Ali Al-jiboory, Abubakr Ayesh, Julian Blank, 
Dmitriy Bryndin, Greg Christian, Kyle Crayne, Ciaron Hamilton, Matt Husband, Changkuk 
Jung, Claire Kopenhafer, Adam Liter, Vanessa Maldonado, Ben Miller, William Muir, Eureka 
Pai, Alicia Parrish, Neil ver Planck, Nick Rekuski, Giacomo Romanini, William Sands, Adam 
Soliman, Erik Stitt,  Eremey Valetov, Matthew Vincent, Michael Wojcik, Stephen Yowono, Ali 
Zare, and Yisu Zhou. A special thank you to Non Thongprong who graciously provided a copy 
of his entire thesis which allowed me to debug some especially subtle spacing 
inconsistencies.

>>>>

\def\msuversion{4.1b}
\def\msudate{2023/05/25}
\title{\textbf{Using the MSU Thesis Class}}
\author{\textbf{Alan Munn}\\Department of Linguistics, Languages, and Cultures\\Michigan State University\\\texttt{\href{mailto:amunn@msu.edu}{amunn@msu.edu}}}
\date{Version \msuversion\\\msudate}
\usepackage{fontspec}
\usepackage[lmargin=.75in,rmargin=.75in,tmargin=1in,bmargin=1in]{geometry}
\usepackage{titling}
\usepackage{array, booktabs, multicol, fancyhdr, xspace,tabularx}
\usepackage{enumitem}
\usepackage{fancyvrb,listings,url}
\usepackage[sf,small]{titlesec}
\usepackage[section]{placeins}
\usepackage[colorlinks=true]{hyperref}
\setmonofont{Inconsolatazi4}

@@

\section{User commands}
In addition to all the user functionality defined by \pkg{memoir}, the \pkg{msu-thesis}\ class defines seven new titling commands, and two “appeasement” commands, i.e., commands to tweak the formatting to appease the the thesis office’s inconsistency.
\begin{table}[htpb]
\centering
\begin{tabularx}{.8\textwidth}{>{\ttfamily}lX}
\toprule
{\bs maketitlepage} & Makes the main title page for the thesis.\\
{\bs fieldofstudy\{\}} &  Takes one argument corresponding to your field of study. For a dual major use the \pkg{\bs dualmajor} command instead.\\
{\bs dualmajor\{\}\{\}} & Takes two arguments, one for each of the two majors.\\
{\bs dedication\{\}} &  Takes one argument (should be short), your dedication.\\
%{\{publicabstract\}} &  Environment for the public abstract (unnumbered, uncounted).\\
{\bs makecopyrightpage} &  Creates the copyright page (use \texttt{\bs makecopyrightpage*} to align the text on the left.)\\
{\bs makededicationpage} &  Creates the dedication page.\\
%{\bs makebibliographypage} &  Creates the bibliography cover page.\\
{\{abbreviations\}} & Environment for the List of Abbreviations \\
{\bs abbrev\{\}\{\}} & add an abbreviation to the list of abbreviations\\
{msutocdepth} & Counter for setting the TOC depth. Default is 1 (sections+chapters). Set this to 0 to use the simplified (chapters only) format that the thesis office suggests but doesn’t require.\\
\bottomrule
\end{tabularx}
\caption{Class titling commands}
\end{table}

\begin{table}[htpb]
\centering
\begin{tabularx}{.8\textwidth}{>{\ttfamily}lX}
\toprule
{\bs msucaptiondelim} &  Delimiter for floating elements (see section \ref{captiondelim}).\\
{\bs msutocdelim} &  Delimiter for table of contents chapter/section titles.\\
%{\bs setabstractnamespace} &  Changes spacing after the name in the abstract (see section \ref{abstractspacing}).\\
\bottomrule
\end{tabularx}
\caption{Appeasement commands}
\end{table}

@@

\subsubsection{New lists and floats}
Note that the thesis office no longer seems to \emph{require} lists of anything other than the main table of contents. This is another odd decision on their part. If do include a List of Tables and List of Figures and need to add other lists, you can follow the directions here. Note that lists of algorithms require special treatment. See §\ref{algorithms}.

If you are using other kinds of floats such as listings, you should use the Memoir |\newlistof| command to make the relevant list. The class provides a macro |\msucaptiondelim| which can be used to make sure the formatting of the captions in the list-of-X match the setting you have for Figures and Tables.  Here is an example of how you would add a listings list. For lists of algorithms, see section \ref{algorithms} below. The following code goes in your preamble:
\begin{quote}
\begin{lstlisting}
\newlistof{listoflistings}{lol}{List of Listings}
\newfloat[chapter]{listing}{lol}{Listing}
\newlistentry{listing}{lol}{0}
\renewcommand*{\cftlistingname}{Listing\space}
\renewcommand*{\cftlistingaftersnum}{\msucaptiondelim}
\end{lstlisting}
\end{quote}

@@

\section{Acknowledgements}
Thanks to Lars Madsen, Ulrike Fischer and Peter Wilson for help with setting up parts of 
the memoir code for versions 1.0--1.4 (now eliminated due to changed requirements). Thanks 
to Wolfgang Sternefeld for supplying the \pkg{linguex}\ spacing fix code, Leo Liu for the 
landscape page numbering code, which greatly simplified my original version. Thanks to 
Florent Chervet for early \pkg{hyperref} code (up until v.3.6), and Ulrike Fischer for the 
current \pkg{hyperref} code.  Thanks also to the following students who have reported 
problems over the years: Irina Agafonova, Ali Al-jiboory, Abubakr Ayesh, Julian Blank, 
Dmitriy Bryndin, Greg Christian, Kyle Crayne, Ciaron Hamilton, Matt Husband, Changkuk 
Jung, Claire Kopenhafer, Adam Liter, Vanessa Maldonado, Ben Miller, William Muir, Eureka 
Pai, Alicia Parrish, Neil ver Planck, Taha Posos, Nick Rekuski, Giacomo Romanini, William Sands, Adam 
Soliman, Erik Stitt,  Eremey Valetov, Matthew Vincent, Michael Wojcik, Stephen Yowono, Ali 
Zare, and Yisu Zhou. A special thank you to Non Thongprong who graciously provided a copy 
of his entire thesis which allowed me to debug some especially subtle spacing 
inconsistencies.
